---
title: "Data Project"
author: Nuoya Zheng
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preparation

```{r}
#Load relevant library
library(vtable)
library(tidyverse)
library(dplyr)
library(purrr)
library(lubridate)
library(jtools)
library(haven)

# Load Most Recent Cohorts Scorecard Elements Data
MRCSED<- read_csv("Most+Recent+Cohorts+(Scorecard+Elements).csv")

# Load ID Name Link Data
ID_N <- read_csv("id_name_link.csv")

# Generate a list total of 12 files Load Google Trends Data
Trends_FL <- list.files(path = "Noah",  pattern = "trends_up_to_", full.names = TRUE) %>% lapply(read_csv) %>%bind_rows


ID_N <-ID_N %>% group_by (schname) %>% mutate(N =n()) %>% filter (N==1)

#Convert the earning variable to numeric
MRCSED$"md_earn_wne_p10-REPORTED-EARNINGS" = as.numeric(as.character(MRCSED$"md_earn_wne_p10-REPORTED-EARNINGS"))

#Rename OPEID in ID for join purpose
names(ID_N)[names(ID_N) == 'opeid'] <- 'OPEID'

#Join ID and ggtrend
trendID <- ID_N %>% left_join(Trends_FL, by = 'schname')

#Rename unitid to UNITID in order to join
trendID  = rename(trendID ,  UNITID = unitid)

#Join trendID with MRCSED
indexScore <-trendID %>% left_join(MRCSED, by = c('UNITID'= 'UNITID','OPEID'='OPEID'))

# Filter out the predominantly grant bachelor colleges
indexScore <-indexScore %>% filter (PREDDEG == 3,na.rm=TRUE)

# Rename md_earn_wne_p10-REPORTED-EARNINGS to median_salary
names(indexScore)[names(indexScore) == 'md_earn_wne_p10-REPORTED-EARNINGS'] <- 'median_salary'

#Standardize the Index, and Group the data by Month and UNITID
indexScore_grouped <- indexScore %>% mutate (date = as.Date(str_sub (monthorweek,1,10))) %>%
  group_by (schname, keyword) %>%
  group_by (month = floor_date(date,"month"), OPEID, median_salary) %>%
  summarize(index = mean (index, na.rm = FALSE))

#Checking for error
sum(is.na(indexScore_grouped))
indexScore_grouped <- drop_na(indexScore_grouped )
sum(is.na(indexScore_grouped))

```

## Building Regression
```{r}

indexScore_grouped <- indexScore_grouped %>% 
  mutate (treated = median_salary >= 50000, post_treatment = month >= as.Date("2015-10-01"))

model <- lm(index ~ treated * post_treatment  , data = indexScore_grouped)
export_summs(model)
#The reason for choosing this model is this model used to analyze the relationship between scorecard release and student interest is the difference-in-difference model, which I named model. Number 50000 is the average. Because scorecard was release on the beginning of September,so I chose date 2015-10-01. In the Difference in Differences (DiD) model, the treated group is median salary, the control group is after, also the release of scorecard is the treatment.

```

## Graph
```{r pressure, echo=FALSE}
ggplot(indexScore_grouped , aes(month, index, color = treated)) +
  stat_summary(geom = 'line') +
  geom_vline(xintercept = as.Date ("2015-10-01")) 

```

## Graph Explanation
For analytics for the graph, True means the universities where earning is above 50k, False means it is below 50k, So we will state and proves that after the release of scorecard, people looked for school with high earning (>50k) more.


## Conclusion
The impact of high-income college graduates and low-income college graduates on the Google Composite Trends Index after graduation shows that the college scorecard increases over time on the impact, from the model, there are 16% more likely that student will shift their interest into the universities that median income after 6 years of graduation is high. So, we reject the null hypothesis, based on the p-value < 0.001. We could assume that there is no statistically significant evidence that the treatment and control groups have the same level of search after treatment. 
